\bf \texttt{forestecology} package for modeling interspecies competition between trees

### 2021-01-20 etc/paper/forestecology.tex
fixed header error
Re-knit manuscript
Added Simon as author

  \author{
        Albert Y. Kim \thanks{Albert Y. Kim is Assistant Professor, Statistical \& Data Sciences,
Smith College, Northampton, MA 01063 (e-mail:
\href{mailto:akim04@smith.edu}{\nolinkurl{akim04@smith.edu}}).} \\
    Program in Statistical \& Data Sciences, Smith College\\
     and \\     David Allen \\
    Biology Department, Middlebury College\\
      }
  \maketitle
} \fi

@@

\hypertarget{add-foldid-to-each-tree}{%
\section{Add foldID to each tree}\label{add-foldid-to-each-tree}}

@@

\hypertarget{remove-empty-folds}{%
\section{Remove empty folds}\label{remove-empty-folds}}

@@

\NormalTok{cv_bw }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{pull}\NormalTok{(.estimate)}
\CommentTok{## [1] 0.1533511}
\end{Highlighting}
\end{Shaded}

>>>>

  \author{
        Albert Y. Kim \thanks{Albert Y. Kim is Assistant Professor, Statistical \& Data Sciences,
Smith College, Northampton, MA 01063 (e-mail:
\href{mailto:akim04@smith.edu}{\nolinkurl{akim04@smith.edu}}).} \\
    Program in Statistical \& Data Sciences, Smith College\\
     and \\     David Allen \\
    Biology Department, Middlebury College\\
     and \\     Simon P. Couch \\
    Mathematics Department, Reed College\\
      }
  \maketitle
} \fi

@@

Then add foldID to each tree

@@

Then remove empty folds

@@

\NormalTok{cv_bw }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{pull}\NormalTok{(.estimate)}
\CommentTok{## [1] 0.1532316}
\end{Highlighting}
\end{Shaded}
